### 2017-03-31 paper/evaluation.tex
pass on text

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
%%\newcommand{\numRQE}{RQ5}
\newcommand{\numRQF}{RQ5}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost is distributed across test cases?}
\newcommand{\RQC}{How often developers provides support to parallel
execution to amortize the execution cost?}
\newcommand{\RQD}{What is the impact of parallelization?}
%%\newcommand{\RQE}{What factors contribute to improve performance
%%  through parallelization?\Jbc{Previously as "When does
%%    parallelization works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of low-level parallelism?}

\begin{itemize}
    \item \textbf{\numRQA.} \RQA
    \item \textbf{\numRQB.} \RQB
    \item \textbf{\numRQC.} \RQC
    \item \textbf{\numRQD.} \RQD
%%    \item \textbf{\numRQE.} \RQE
    \item \textbf{\numRQF.} \RQF
\end{itemize}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses the relationship of test cases and the overall execution
cost: we are interested to investigate how the execution time is
distributed among test cases.  In the third research question, we
investigate if developers consider low-level parallelism features
available out-of-the-box (see Section~\ref{sec:modes}). In addition,
we want to identify what configurations are often used and why they
are more popular (if any).  The fourth research question addresses the
impact of low-level parallelism on test execution from projects in our
sample set. We want to identify subjects that already use test
parallelization and compare their performance in contrast to
sequential execution. In addition, we are interested in evaluating the
performance of sequential test suites with different parallelization
settings.
Finally, the fifth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

@@

To evaluate the support of parallelization to run tests, we
investigate if there are projects with parallel execution enabled by
default and what configurations are more popular. In addition, we
complement our investigation by analyzing several build files (\ie,
\pomf{}) to identify projects that supports parallel execution but
require additional execution parameters to enable this feature.  We
describe our approach as follows:

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that \Jbc{summarize results from both parts (static and
      dynamic)}.} 
  \end{minipage}
}
\end{center}

>>>>

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
\newcommand{\numRQF}{RQ5}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost is distributed across test cases?}
\newcommand{\RQC}{How often developers provides support to parallel
execution of test suites?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQF}{What are the limitations of low-level parallelism?}

\begin{itemize}
    \item \textbf{\numRQA.} \RQA
    \item \textbf{\numRQB.} \RQB
    \item \textbf{\numRQC.} \RQC
    \item \textbf{\numRQD.} \RQD
    \item \textbf{\numRQF.} \RQF
\end{itemize}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses the relationship of test cases and the overall execution
cost: we are interested to investigate how the execution time is
distributed among test cases.  In the third research question, we
investigate if developers consider low-level parallelism features
available out-of-the-box to amortize test execution (see
Section~\ref{sec:modes}). In addition, we want to identify what
configurations are often used and why they are more popular (if any).
The fourth research question addresses the impact of low-level
parallelism on test execution from projects in our sample set. We want
to identify subjects that already use test parallelization and compare
their performance in contrast to sequential execution. In addition, we
are interested in evaluating the performance of sequential test suites
with different parallelization settings.
Finally, the fifth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

@@

To evaluate the support of parallel execution of test suites, we
considered the \numMedLong{} projects that ran in at least one minute
identified in Section~\ref{sec:rqA} (\ie, \medg{} and \longg{}
groups). We are interested to know if developers consider low-level
parallelism features to amortize the execution cost. More precisely,
we investigate if there are projects with parallelism configuration
enabled by default or if developers configure this feature to run only
on specific scenarios (\eg, dedicated server).  We describe our
approach as follows:

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused given that only \Fix{\%}
      of projects supports parallel execution of test suites.}
  \end{minipage}
}
\end{center}
